Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-26 paper.tex
a very rough intro completed

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}

@@

        \section{Big neuroimaging Datasets}\label{datasets}
            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of a singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example of 
            such an image is the BigBrain \note{cite here}, a histological image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM), polarized light images (PLI) and micro coherence 
            tomography (microCT) \note{need to do more research here}. Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

@@

        \section{Infrastructure}\label{infrastructure}

>>>>

\usepackage{titlesec}
\titleformat{\chapter}
  {\normalfont\LARGE\bfseries}{\thechapter}{1em}{}
\titlespacing*{\chapter}{0pt}{3.5ex plus 1ex minus .2ex}{2.3ex plus .2ex}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} 
\usepackage{xcolor} 
\usepackage{ulem}

@@

        \section{Big neuroimaging Datasets}\label{datasets}
            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of a singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example of 
            such an image is the BigBrain \note{cite here}, a histological image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM), polarized light images (PLI) and micro coherence 
            tomography (microCT) \note{need to do more research here.cite}. 
            Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

@@

        \section{Infrastructure}\label{infrastructure}
            HPC infrastructure was designed durign a time when compute resources
            were scarce. As a result, resource managers for these systems employ
            strategies to efficiently use the compute resources available for 
            processing. However, with the advent of big data, there has been a 
            shift from compute-intensive to data-intensive workloads. That is, 
            with the accumulation of large datasets, data transfers have begun 
            to monopolize processing time, and with it software has been 
            designed to minimize data transfers.

            We define HPC systems as those that employ shared parallel 
            filesystem such as Lustre. This shared filesystem is the slowest of
            all storage devices as it is shared amongst all users of the system.
            Compute nodes in an HPC system may or may not contain any local 
            storage and network interconnects between nodes are typically fast.
            Resources managers used in HPC infrastructures typically employ 
            batch scheduling and execute heterogenous workflows. 
            Examples of schedulers used in HPC clusters 
            include SLURM, PBS, SGE and HTCondor \note{cite here}.

            Commodity infrastructure differs from HPC infrastructures in that
            it uses less-costly hardware. It follows a shared-nothing paradigm
            where the storage is not shared between nodes. That is all compute
            nodes are responsible for storing the data as well. File systems
            used in these clusters are distributed filesystems, such as the
            Hadoop Distributed File System (HDFS) and Alluxio \note{cite}.
            Fault-tolerance of the data is achieved through replication across
            nodes. As transferring data across the network is typically costly 
            in such infrastructures, frameworks designed to run on commodity 
            infrastructure attempt to limit the transfer of data across nodes. 
            Resource managers created specifically for these systems
            typically expect dedicated infrastructure, as is the case with 
            Yet Another Resource Negotiator (YARN), but can also execute 
            heterogeneous workflows, as can be seen with Mesos \note{cite}.

            Commodity clusters may also come in the form of cloud infrastructure
            . While the hardware employed is typically the same as other
            commodity clusters, the software used varies. Cloud infrastructures
            have the added benefit of virtualization, allowing users to 
            configure the infrastructure and software requirements to meet their
            needs. Cloud infrastructure also enables researchers to request
            dedicated resources without having to maintain these resources. One
            of the biggest limiting factors of cloud resources is the cost 
            associated with usage.

            Researchers typically have access to HPC infrastructure, but may
            also have access to commodity infrastructure in the format of a 
            local cluster or cloud. Although both neuroimaging frameworks and
            big data frameworks can be made to execute in either environments,
            the performance improvements that they bring are very much 
            dependent on infrastructure that they are executed on. For instance,
            neuroimaging workflows typically read and write to a shared file
            system at each workflow step. This is less of an issue in HPC 
            infrastructure as network bandwidth is typically better than on 
            commodity infrastructure. In contrasts, Big Data framework typically
            rely on there being some form of local storage. Employing a Big Data
            framework on HPC infrastructure may in turn result in less to no 
            data locality -- a strategy employed by Big Data frameworks to 
            minimize data movement across the network. Due to the variability in
            infrastructure available to researchers, a workflow framework good
            for neuroscience must be well adapted to handle these differences.
